Software Citation Principles

### 2016-07-26 sc-principles/rebuttal/rebuttal.tex

\item \textbf{Reviewer comment:}
\emph{line 89: ``We expect that this discussion may lead to a second, final version'': So this paper is not the final version? Please clarify.}

\textbf{Our response:}
Thank you for pointing this error out. We have corrected this statement to indicate that the past discussion led to a second version (what was submitted).

\item \textbf{Reviewer comment:}
\emph{line 97: ``the need for credit for application software underscores the need to overhaul the system of credit for all research products.'': Very true and very important. But then maybe the concept of a ``citation'' is obsolete altogether, and we shouldn't be advocating ``software citations'', but something new altogether? Some more discussion on this would be valuable, I think. This relates to my comment above about a long-term vision.}

\textbf{Our response:}
We have added new language to the Motivation section (\S 2) describing what a
more complete solution might look like, and also included an additional sentence
and citation to existing work on this topic towards the end of \S 3.

### 2016-07-26 sc-principles/rebuttal/rebuttal.tex

\begin{enumerate}
\item \textbf{Reviewer comment:}
\emph{The logical connections between the different parts of the paper are not clear. For example, how do the ``basic requirements'' of Table 2 map to the ``principles'' in Section 1? And are the principles presented in the beginning the *outcome* of this research (this is what lines 29+ seem to suggest) or are they *assumptions* of the approach to be discussed and evaluated (this is how they seem to be treated in Section 5).}

\textbf{Our response:}
We view the principles presented at the beginning as the main outcomes\slash results of this work, with the process of producing them (discussed in the new Section 3) based on a synthesis of information from the use cases and related work. Then, Section 6 (previously 5) discusses the ``results''.
Our modifications to the structure of the paper, and changes we hope improve the logical flow, should help indicate these connections better.

\item \textbf{Reviewer comment:}
\emph{It is not clear whether the authors consider software citations to be just the first step towards a long-term vision, or whether they consider software citations the overall final solution. It seems that the first is the case, but the long-term vision is not discussed.}

\textbf{Our response:}
Ultimately we believe that software citation is just a part of a more complete
solution for the sharing and citation of all products of scholarly research.
We have updated the language in the first paragraph of \S 2 to reflect this.

### 2016-07-26 sc-principles/software-citation-principles.tex
some wording fix at beginning of motivation

As the process of research\footnote{We use the term ``research'' in this document to include work intended to increase human knowledge and benefit society, in science, engineering, humanities, and other areas.} has become increasingly digital, research outputs
and products have grown beyond simply papers and books to include software,
data, and other electronic components such as presentation slides, posters,
(interactive) graphs, maps, websites (e.g., blogs and forums), and multimedia
(e.g., audio and  video lectures).  Research knowledge is embedded in these
components. And papers and books themselves are also becoming increasingly
digital, allowing them to become executable and reproducible. As we move towards
this future where research is performed in and recorded as a variety of linked
digital products, the characteristics and properties that developed for books
and papers need to be applied to all digital products and possibly adjusted.
Here, we are concerned specifically with the citation of software products. The
challenge is not just the textual citation of software in a paper, but the more
general identification of software used within the research process. This work is
focused on making software a citable entity throught the scholarly ecosystem. While
software products are a relatively small fraction of the sum total of
research output, this work together with other efforts such as the Force11
Data Citation Principles~\cite{data-citation-principles} collectively represent
an effort to better describe all outputs of research.

>>>>

As the process of research\footnote{We use the term ``research'' in this document to include work intended to increase human knowledge and benefit society, in science, engineering, humanities, and other areas.} has become increasingly digital, research outputs
and products have grown beyond simply papers and books to include software,
data, and other electronic components such as presentation slides, posters,
(interactive) graphs, maps, websites (e.g., blogs and forums), and multimedia
(e.g., audio and  video lectures).  Research knowledge is embedded in these
components. And papers and books themselves are also becoming increasingly
digital, allowing them to become executable and reproducible. As we move towards
this future where research is performed in and recorded as a variety of linked
digital products, the characteristics and properties that developed for books
and papers need to be applied to all digital products and possibly adjusted.
Here, we are concerned specifically with the citation of software products. The
challenge is not just the textual citation of software in a paper, but the more
general identification of software used within the research process. This work is
focused on making software a citable entity in the scholarly ecosystem. While
software products represent a small fraction of the sum total of
research output, this work together with other efforts such as the FORCE11
Data Citation Principles~\cite{data-citation-principles,10.7717/peerj-cs.1}
collectively represent an effort to better describe (and cite) all outputs of
research.
